% This document utilises the "moderncv" package for LaTeX
% http://www.ctan.org/pkg/moderncv
% Test

\documentclass[11pt,a4paper]{moderncv}
% \moderncvtheme[red]{classic}				% classic or banking
\moderncvtheme[blue]{banking}				% classic or banking
% \definecolor{color1}{RGB}{255,85,0}		% custom orange colour
\usepackage[utf8]{inputenc}
%\usepackage[scale=0.8]{geometry}
\usepackage[top=0.9cm, bottom=0.8cm, left=2cm, right=2cm ]{geometry}

% Prevent page breaks within sections/paragraphs
\widowpenalties 1 10000
\raggedbottom

\usepackage{tabularx}
\usepackage{multicol}
% \usepackage{hyperref}
% \hypersetup{colorlinks,breaklinks,urlcolor=color1, linkcolor=color1}


\firstname{Edgar}
\familyname{Ivanov}
%\address{Flat 3, Fonda Court, 3 Premiere Place}{London, E14 8SD}
\address{Flat 21, Mazoji 7}{Kaunas, LT-45307}
\phone{+370 605 6232}
\email{ivanovedgar@gmail.com}
\homepage{www.ivanovedgar.me}
%\title{IT Admin}

% ----------------------------------------------------------------------------------
%            content
% ----------------------------------------------------------------------------------
\begin{document}
\maketitle
\section{Profile}
\cvline{}{Tenacious Computer Science graduate with genuine passion for hardware and proven troubleshooting skills gained during the Industrial Placement with Information Services department of Aberystwyth University and the following year spent working in first line customer support.}

\section{Key Achievements and Skills}

\cvline{}{\begin{multicols}{2}
\begin{itemize}
    \item Certified Apple Macintosh Technician
    \item Knowledge of the Active Directory and Exchange
    \item PowerShell scripting
    \item VM monitoring using PRTG and custom build scripts
    \item Networked equipment setup and management
    \item Windows/Unix Server configuration
    \item Limited AWS knowledge R53, S3, EC
    \item Windows OS Deployment with WDS/WAIK
    \item SNMP Network Management System
    \item Roll-out of 3CX VoIP phone system
    \item Repairing IT equipment and replacing parts
    %\item \LaTeX
	%\item VCS: Git/SVN
	%\item Eclipse/NetBeans
	%\item Android/Java SDK
\end{itemize}
\end{multicols}}

\subsection{Programming Languages}
\cvline{}{\begin{multicols}{3}
\begin{itemize}
	%\item ROR
	\item PowerShell
	\item Java
	\item C/C++
	\item Assembler
	%\item PHP/Perl
	\item HTML5/XHTML/CSS
	\item SQL (MySQL/PostgreSQL)
	%\item JavaScript/JSON
\end{itemize}
\end{multicols}}

\section{Education}
\cventry
	{September 2010 - June 2014}{BSc (Hons) Mobile And Wearable Computing, 2:2}
	{Aberystwyth University}{Aberystwyth, UK}
	\newline
	{\textit{Inc Integrated Industrial And Professional Training}}{}
	\cvline{}{
	\begin{multicols}{0}
	\begin{itemize}
      %  \item 2:1 - Agile Methodologies (XP, FDD, AntiPatterns, Refactoring)
      %  \item 2:2 - Ubiquitous Computing
      %  \item 2:2 - Open Source Development Issues (Licensing, Patents, Cathedral, Bazaar)
      %  \item 2:2 - Developing Internet Based Applications (ROR, Cryptography \& Security)
      %  \item 2:1 - Software Development Life Cycle (Group project app for Android)
        \item System and Network Administration (74)
        \item Computer Architecture And Hardware (76)
        \item Modelling Persistent Data (59)
        \item C And Unix Programming (60)
        \item Computer Hardware \& Operating Systems (64)
        \item Mathematics (70)
      %  \item 1$^{st}$ - Mathematics
      %  \item 2:1 - Databases (MS Access)
      %  \item 2:1 - Intro to Programming (Java)
      %  \item 2:1 - Personal Development
      %  \item 2:1 - Web Development (XHTML/CSS/JS/PHP)
	\end{itemize}
	\end{multicols}
}

\cventry
	{September 1998 - June 2010}{Secondary Education}
	{A. Pushkin Gymnasium}{Kaunas, Lithuania}
	{}{}
	\cvline{}{	
		\begin{multicols}{2}
		\begin{itemize}
			\item A level equivalent
				\begin{itemize}
						\item English A (62) 
						\item History B (49)
						\item Lithuanian A (50)     
				\end{itemize}
			\item 11 GCSE equivalent grades A* - C
				\begin{itemize}
						\item IT (A)
						\item Physics (A)
						\item History  (A)
				\end{itemize}     
		\end{itemize}	
		\end{multicols}}
		
\section{Work Experience}

\cventry
	{October 2015 - Present}{IT System Administrator}
	{VISMA, DIASP}{Vilnius, LT}
	{}{
        \begin{itemize}
            \item Provided 2$^{nd}$ and 3$^{rd}$ line IT support.
            \item VMWare based infrastructure management with 500+ VMs
            \item AD, Exchange, VMWare configuration and management using PowerShell
            \item Monitoring improvement project implementation using PRTG.
            \item Virtual application delivery using Citrix XenApp and MS RDS.
            \item Exchange \& SQL server backup management and troubleshooting.
            \item Disaster recovery and backup planning according to the ISAE standards.
        \end{itemize}
        }

\cventry
	{July 2014 - October 2015 }{Junior Operations/IT Specialist}
	{SECRETSALES.com}{London, UK}
	{}{
        \begin{itemize}
            \item Provided 1$^{st}$ , 2$^{nd}$ and 3$^{rd}$ line IT support.
            \item Vitalization using VB, KVM and VMware
            \item Windows Server with AD, Exchange, GPO, DHCP configuration and management
            \item Producing reports using SQL
            \item Server hardware planning \& implementation, troubleshooting and maintenance.
            \item Administered JIRA Service desk and documented infrastructure configuration in Confluence
            \item GNU/UNIX system administration (setting up MySQL, Apache, VPN)
            \item Asset management
        \end{itemize}
    }
    
\cventry
	{August 2013 - June 2014}{Customer Services Assistant}
	{Aberystwyth University, Information Services}{Aberystwyth, UK}
	{}{
        \begin{itemize}
            \item Provided 1$^{st}$ line IT support, by phone and face to face.
            \item Troubleshooted problems with customer laptops and phones at the desk.
            \item Provided guidance on the use of the IS services.
            \item Focused at being my best every day for the customers, learned to listen actively and communicate effectively.
        \end{itemize}
    }
	
\cventry
	{July 2012 - August 2013}{Industrial Year Placement}
	{Aberystwyth University, Information Services}{Aberystwyth, UK}
	{}{
        \begin{itemize}
            \item Provided 1$^{st}$ and 2$^{nd}$ line IT support.
            \item Carried out computer and ICT equipment maintenance in workshop and on client site.
            \item Installed and upgraded hardware and peripherals.
            \item Identified, investigated and documented solutions to all the types of computing problems.
            \item Developed strong time management and problem solving skills.
            \item Built the deep knowledge of Apple Mac Computers and Windows Server configuration. 
        \end{itemize}
    }
    
\cventry
	{June 2011 - July 2012 }{Crew Member}
	{McDonald's Restaurant}{Aberystwyth, UK}
	{}{
    	\begin{itemize}
           \item Greeted customers, took and assembled orders and received payments.
           \item Followed restaurant's sanitation procedures and policies.
           \item Checked equipment to ensure it was working efficiently.
           \item Gained communication, teamwork and customer services skills.
           \item Learnt how to be a good McDonald's slave.
    	\end{itemize}
	}
	
\section{Personal Projects}
\cventry
	{July 2012 - August 2013}{My Industrial Year Placement blog}
	{\href{http://ivanovedgar.wordpress.com/}{ivanovedgar.wordpress.com/}}{}
	{}{}
\cventry
	{Present}{Contains personal projects and university assignments}
	{\href{http://github.com/ivanovedgar}{github.com/ivanovedgar}}{}
	{}{}

\section{Interests}
\cvline{}{I have a keen interest in new technologies and enjoy reading IT journals in my spare time, mainly focusing on hardware development. Working with open source projects related to the CMS, home media servers and Raspberry Pi. I also own a VPS that hosts my personal website and is being used for VPN. Enjoy hiking with friends and regularly explore National Trust places in the holidays.}

\section{Languages}
\cvlanguage{English}{Fluent}{}
\cvlanguage{Russian}{Native}{}
\cvlanguage{Lithuanian}{Native}{}


\section{References}
\begin{minipage}[b]{0.45\linewidth}
\cvline{Jan Litton}{Team leader}
\cvline{}{Information Services Department}
\cvline{}{Hugh Owen Building, D.7}
\cvline{}{Aberystwyth University}
\cvline{}{Penglais, Aberystwyth, Ceredigion}
\cvline{}{SY23 3DZ}
\cvline{E-Mail}{jpl@aber.ac.uk}
%\cvline{Phone}{}

\end{minipage}
\hspace{1.25cm}
\begin{minipage}[b]{0.55\linewidth}
\cvline{Krystian Galutowski}{Technology Director}
\cvline{}{Technology Department}
\cvline{}{Newcombe House}
\cvline{}{SECRETSALES.com}
\cvline{}{45 Notting Hill Gate, London}
\cvline{}{W11 3LQ}
\cvline{E-Mail}{Krystian.Galutowski@SecretSales.com}
%\cvline{Phone}{}
\end{minipage}

\end{document}